# Lecture 13: Modals
`r Sys.Date()`

````{r echo = FALSE}
htmltools::includeHTML("../../index_lectures.html")
````


## Overview

In this lecture, we will learn about modals in Bootstrap. Modals are a type
of dialog box that can be used to display content, messages, forms, or other
elements on a web page. Modals are commonly used to provide users with
additional information, gather input, or confirm actions. Modals are designed
to be unobtrusive and can be easily customized to match the style and design
of the website. In Bootstrap, modals can be easily added to a web page using
simple HTML and CSS classes.


## Topics Covered

- Introduction to modals
- Using modals in Bootstrap


## Introduction to modals

Modals are a type of dialog box that can be used to display content,
messages, forms, or other elements on a web page. Modals are designed to be
unobtrusive and can be easily customized to match the style and design of the
website. Modals are commonly used to provide users with additional
information, gather input, or confirm actions. Modals are typically displayed
as a pop-up box that appears on top of the main content of the page and
requires the user to interact with it before continuing.

Modals are a versatile tool that can be used for a variety of purposes, such
as displaying notifications, alerts, forms, images, videos, or other content.
Modals can be triggered by clicking on a button, link, or other element on
the page, and can be easily customized to match the style and design of the
website. In Bootstrap, modals can be easily added to a web page using simple
HTML and CSS classes.


### Using modals

To add a modal to a web page in Bootstrap, you can use the `modal` class and
the `data-toggle` attribute. The `modal` class specifies that the element is
a modal, while the `data-toggle` attribute tells Bootstrap to enable the
modal functionality on the element. You can also add additional attributes to
customize the appearance and behavior of the modal, such as the size,
position, animation, and content of the modal.

Here is an example of how to create a simple modal in Bootstrap:

```html
<div class="modal fade" id="exampleModal" tabindex="-1" aria-labelledby="exampleModalLabel" aria-hidden="true">
 <div class="modal-dialog">
  <div class="modal-content">
  <div class="modal-header">
  <h5 class="modal-title" id="exampleModalLabel">Modal title</h5>
 <button type="button" class="btn-close" data-bs-dismiss="modal" aria-label="Close"></button>
</div>
<div class="modal-body">
Modal content goes here...
</div>
<div class="modal-footer">
<button type="button" class="btn btn-secondary" data-bs-dismiss="modal">Close</button>
<button type="button" class="btn btn-primary">Save changes</button>
</div>
</div>
</div>
</div>
```

In this example, the modal is defined using the `modal` class and the `fade`
class to add a fade effect when the modal is displayed. The `id` attribute
specifies the unique identifier of the modal, while the `tabindex`,
`aria-labelledby`, and `aria-hidden` attributes provide additional
accessibility information. The modal content is defined within the
`modal-dialog` and `modal-content` classes, and includes a header, body, and
footer section. The header section contains the title of the modal, the body
section contains the content of the modal, and the footer section contains
buttons for closing or saving changes in the modal.


## Summary

Modals are a versatile tool that can be used to display content, messages,
forms, or other elements on a web page. Modals are commonly used to provide
users with additional information, gather input, or confirm actions. Modals
are designed to be unobtrusive and can be easily customized to match the
style and design of the website. In Bootstrap, modals can be easily added to
a web page using simple HTML and CSS classes. By customizing modals in
Bootstrap, you can create unique and visually appealing dialog boxes that
enhance the user experience and provide valuable functionality.


## Instructions

1. Open the "index.html" file in the lecture directory.
1. Explore the examples of modals in Bootstrap.

## Resources

- [Bootstrap Modals](https://getbootstrap.com/docs/5.1/components/modal/)


````{r echo = FALSE}
htmltools::includeHTML("../../index_lectures.html")
````

