# Lecture 3: Buttons
`r Sys.Date()`

````{r echo = FALSE}
htmltools::includeHTML("../../index_lectures.html")
````


## Overview

In this lecture, we will cover the basics of buttons in Bootstrap 5. Buttons
are an essential component of web design and are used to trigger actions,
such as submitting forms, navigating to different pages, or performing other
interactive tasks. We will explore the different button styles, sizes, and
states provided by Bootstrap and learn how to create attractive and
interactive buttons for your web pages.

## Topics Covered

- Basic buttons
- Anchor tag buttons
- Button sizes
- Button styles
- Grouped buttons

## About Buttons

Buttons are interactive elements that allow users to perform actions on a web
page. They are commonly used for submitting forms, navigating to different
pages, or triggering other interactive tasks. Bootstrap provides a range of
button styles, sizes, and states that allow you to create attractive and
interactive buttons for your web pages.

## Basic Buttons

Bootstrap provides a range of button styles that you can use to create
attractive and interactive buttons for your web pages. These styles include
primary, secondary, success, danger, warning, info, light, and dark buttons.
You can also customize the appearance of buttons by adding additional
classes, such as outline buttons, disabled buttons, and button groups.

Here is an example of how to create a primary button in Bootstrap:

```html
<button type="button" class="btn btn-primary">Primary Button</button>
```

## Anchor Tag Buttons

Bootstrap allows you to create buttons using anchor tags (`<a>` elements)
with the `.btn` class. This allows you to create interactive buttons that can
be styled and customized using Bootstrap's button classes. Anchor tag buttons
are useful for creating links that trigger actions or navigate to different
pages.

Here is an example of how to create an anchor tag button in Bootstrap:

```html
<a href="#" class="btn btn-primary">Primary Button</a>
```

## Button Sizes

Bootstrap provides a range of button sizes that you can use to create buttons
of different sizes. These sizes include small, large, and block-level
buttons. By using these sizes, you can create buttons that fit the design of
your web page and provide a consistent user experience.

Here is an example of how to create a large button in Bootstrap:

```html
<button type="button" class="btn btn-primary btn-lg">Large Button</button>
```

## Button Styles

Bootstrap provides a range of button styles that you can use to create
attractive and interactive buttons for your web pages. These styles include
primary, secondary, success, danger, warning, info, light, and dark buttons.
You can also customize the appearance of buttons by adding additional
classes, such as outline buttons, disabled buttons, and button groups.

Here is an example of how to create a success button in Bootstrap:

```html
<button type="button" class="btn btn-success">Success Button</button>
```

## Grouped Buttons

Bootstrap allows you to group buttons together using the `.btn-group` class.
This allows you to create sets of related buttons that are visually grouped
together. You can also create button toolbars and button dropdowns using
Bootstrap's button group classes.

Here is an example of how to create a button group in Bootstrap:

```html
<div class="btn-group" role="group" aria-label="Basic example">
 <button type="button" class="btn btn-primary">Left</button>
<button type="button" class="btn btn-primary">Middle</button>
<button type="button" class="btn btn-primary">Right</button>
</div>
```

## Summary

In this lecture, we covered the basics of buttons in Bootstrap 5. We explored
the different button styles, sizes, and states provided by Bootstrap and
learned how to create attractive and interactive buttons for web pages. By
using Bootstrap's button classes and utilities, you can easily create buttons
that fit the design of your web page and provide a consistent user
experience.

## Instructions

1. Open the "index.html" file in the lecture directory.
1. Browse through the different button styles, sizes, and states.

## Resources

- [Basic buttons](https://getbootstrap.com/docs/5.0/components/buttons/)
- [Anchor tag
  buttons](https://getbootstrap.com/docs/5.0/components/buttons/#anchor-tags)
- [Button
  sizes](https://getbootstrap.com/docs/5.0/components/buttons/#sizing)
- [Button
  styles](https://getbootstrap.com/docs/5.0/components/buttons/#examples)
- [Grouped
  buttons](https://getbootstrap.com/docs/5.0/components/button-group/)


````{r echo = FALSE}
htmltools::includeHTML("../../index_lectures.html")
````

