# Lecture 2: Typography and Colors
`r Sys.Date()`

```{r echo = FALSE}
htmltools::includeHTML("../../index_lectures.html")
htmltools::includeHTML("../../index_exercises.html")
```


## Overview

In this lecture, we will cover the basics of typography and colors in
Bootstrap 5. We will explore the different typography utilities and color
classes provided by Bootstrap. We will also discuss how to use these
utilities to style text and backgrounds in your web pages.

## Topics Covered

- Typography utilities in Bootstrap 5
- Color classes in Bootstrap 5
- Styling text and backgrounds

## Resources

- [Bootstrap typography](https://getbootstrap.com/docs/5.0/content/typography/)
- [Bootstrap headings](https://getbootstrap.com/docs/5.0/content/typography/#headings)
- [Bootstrap display headings](https://getbootstrap.com/docs/5.0/content/typography/#display-headings)
- [Bootstrap lead](https://getbootstrap.com/docs/5.0/content/typography/#lead)
- [Bootstrap inline text elements](https://getbootstrap.com/docs/5.0/content/typography/#inline-text-elements)
- [Bootstrap text colors](https://getbootstrap.com/docs/5.0/utilities/colors/#colors)
- [Bootstrap background colors](https://getbootstrap.com/docs/5.0/utilities/colors/#background-color)
- [Emmet Abbreviation Lorem Ipsum generation](https://docs.emmet.io/abbreviations/lorem-ipsum/)

## Instructions

1. Open the "index.html" file in the lecture directory.
1. Browse through the different typography utilities and color classes.


```{r echo = FALSE}
htmltools::includeHTML("../../index_lectures.html")
htmltools::includeHTML("../../index_exercises.html")
```

