# Lecture 4: Utility Classes
`r Sys.Date()`

````{r echo = FALSE}
htmltools::includeHTML("../../index_lectures.html")
htmltools::includeHTML("../../index_exercises.html")
````


## Overview

In this lecture, we will cover utility classes in Bootstrap 5. Utility classes
are a set of predefined CSS classes that can be used to apply common styles
and properties to elements in your web pages. These classes provide a quick
and easy way to add styling without writing custom CSS code. We will explore
some of the most commonly used utility classes in Bootstrap and learn how to
leverage them to enhance the design and layout of your web pages.

## Topics Covered

- Text utilities
- Spacing utilities
- Sizing utilities

## About Utility Classes

Utility classes are a set of predefined CSS classes that can be used to apply
common styles and properties to elements in your web pages. These classes
provide a quick and easy way to add styling without writing custom CSS code.
Bootstrap includes a wide range of utility classes that can be used to style
text, spacing, sizing, and more. By using these classes, you can enhance the
design and layout of your web pages and create a consistent and professional
look.

## Text Utilities

Bootstrap provides a range of text utilities that allow you to style text in
your web pages. These utilities include text alignment, text wrapping, text
transformation, and text decoration classes. By using these classes, you can
customize the appearance of text elements and create visually appealing
content.

Here is an example of how to use text utilities in Bootstrap:

```html
<p class="text-center">Centered text</p>
<p class="text-uppercase">Uppercase text</p>
<p class="text-decoration-underline">Underlined text</p>
<p class="text-wrap">Wrapped text</p>
```

## Spacing Utilities

Spacing utilities in Bootstrap allow you to add margin and padding to elements
in your web pages. These utilities include classes for adding margin and
padding to the top, bottom, left, and right sides of an element. By using
these classes, you can create space between elements and control the layout of
your web pages.

Here is an example of how to use spacing utilities in Bootstrap:

```html
<div class="mt-3">Margin top</div>
<div class="mb-3">Margin bottom</div>
<div class="ml-3">Margin left</div>
<div class="mr-3">Margin right</div>
<div class="pt-3">Padding top</div>
<div class="pb-3">Padding bottom</div>
<div class="pl-3">Padding left</div>
<div class="pr-3">Padding right</div>
```

## Sizing Utilities

Sizing utilities in Bootstrap allow you to control the size of elements in your
web pages. These utilities include classes for setting the width and height of
elements, as well as classes for controlling the maximum and minimum width and
height. By using these classes, you can create responsive and well-proportioned
designs that adapt to different screen sizes.

Here is an example of how to use sizing utilities in Bootstrap:

```html
<div class="w-50">Width 50%</div>
<div class="h-50">Height 50%</div>
<div class="mw-50">Max-width 50%</div>
<div class="mh-50">Max-height 50%</div>
<div class="minw-50">Min-width 50%</div>
<div class="minh-50">Min-height 50%</div>
```
 

## Instructions

1. Open the "index.html" file in the lecture directory.
1. Explore the different utility classes and their applications.

## Resources

- [Text utilities](https://getbootstrap.com/docs/5.0/utilities/text/)
- [Spacing utilities](https://getbootstrap.com/docs/5.0/utilities/spacing/)
- [Sizing utilities](https://getbootstrap.com/docs/5.0/utilities/sizing/)


````{r echo = FALSE}
htmltools::includeHTML("../../index_lectures.html")
htmltools::includeHTML("../../index_exercises.html")
````

