# Lecture 4: Utility Classes
`r Sys.Date()`

```{r echo = FALSE}
htmltools::includeHTML("../../index_lectures.html")
htmltools::includeHTML("../../index_exercises.html")
```


## Overview

In this lecture, we will cover utility classes in Bootstrap 5. Utility classes
are a set of predefined CSS classes that can be used to apply common styles
and properties to elements in your web pages. These classes provide a quick
and easy way to add styling without writing custom CSS code. We will explore
some of the most commonly used utility classes in Bootstrap and learn how to
leverage them to enhance the design and layout of your web pages.

## Topics Covered

- Text utilities
- Spacing utilities
- Sizing utilities

## Resources

- [Text utilities](https://getbootstrap.com/docs/5.0/utilities/text/)
- [Spacing utilities](https://getbootstrap.com/docs/5.0/utilities/spacing/)
- [Sizing utilities](https://getbootstrap.com/docs/5.0/utilities/sizing/)

## Instructions

1. Open the "index.html" file in the lecture directory.
1. Explore the different utility classes and their applications.


```{r echo = FALSE}
htmltools::includeHTML("../../index_lectures.html")
htmltools::includeHTML("../../index_exercises.html")
```

