# Lecture 1: Introduction and Setup of Bootstrap 5
`r Sys.Date()`

```{r echo = FALSE}
htmltools::includeHTML("../../index_lectures.html")
htmltools::includeHTML("../../index_exercises.html")
```


## Overview

In this lecture, we will cover the basics of Bootstrap 5 and its key
features. We will also discuss how to set up a Bootstrap project and explore
the various components and utilities provided by Bootstrap. An initial HTML
template will be produced that will be utilized and expanded upon during the
lectures. Please note that many, if not all, keyboard shortcuts are VSCode
specific and probably will not function the same in other software or text
editors.

## Topics Covered

- Introduction to Bootstrap 5
- Easily setting up a Bootstrap 5 project

## Resources

- [VSCode](https://code.visualstudio.com/) (Visual Studio Code)
- Provided that you have installed VSCode, add the "Live Server" extension
  within VSCode!
- [Emmet Abbreviation in
  VSCode](https://code.visualstudio.com/docs/editor/emmet)
- [Bootstrap
  Documentation](https://getbootstrap.com/docs/5.0/getting-started/introduction/)
- [Bootstrap Examples](https://getbootstrap.com/docs/5.0/examples/)
- [CDN via jsDelivr
  links](https://getbootstrap.com/docs/5.0/getting-started/download/#cdn-via-jsdelivr)
- [Bootstrap Native Font
  Stack](https://getbootstrap.com/docs/5.0/content/reboot/#native-font-stack)
- [Web browser font
  defaults](https://granneman.com/webdev/coding/css/fonts-and-formatting/web-browser-font-defaults)
- [Mozilla Horizontal Rule
  Tag](https://developer.mozilla.org/en-US/docs/Web/HTML/Element/hr)

## Instructions

1. Download VSCode and add the "Live Server" extension. Note that other text
   editors can of course also be used, but the content herein will primarily
   be presented using VSCode
1. Make sure a new file named "index.html" exists in your directory
1. VSCode specific: Create a boilerplate HTML document by typing "doc" and
   hitting tab.
1. Revise the title in the HTML head to your liking
1. Create a h1 title in the HTML body to your liking. You can just type "h1"
   and hit tab to add the tag (using built in extension Emmet Abbreviation in
   VSCode)
1. Check out the font style in your browser. Too see a list of default
   browser fonts, check out [this
   link](https://granneman.com/webdev/coding/css/fonts-and-formatting/web-browser-font-defaults).
   Internet Explorer and Chrome uses Courier New.
1. Use [CDN via jsDelivr
   links](https://getbootstrap.com/docs/5.0/getting-started/download/#cdn-via-jsdelivr)
   to add the CSS to your HTML head and the JavaScript to the bottom of the
   body. We will add bootstrap differently in later lectures to be able to
   customize it
1. Now you are able to use Bootstrap classes and components in your file!
1. Check out the font style again in your browser. Note that the font has now
   changed. The default font stack is provided in [this
   link](https://getbootstrap.com/docs/5.0/content/reboot/#native-font-stack)


```{r echo = FALSE}
htmltools::includeHTML("../../index_lectures.html")
htmltools::includeHTML("../../index_exercises.html")
```

